Project Report

### 2022-01-12 Gandhi_Project_Report/draft3.tex
fiddling with bib loading

\textbf{NB NB FINISH}
\begin{Example}
  For example $\phi(x)=\sin(\frac{\pi}{2}x)^2$ is a conjugacy between two systems $Tu=1-|2u-1|$ and $Sv=4v(1-v)$  defined on $U=[0,1]$.

  To see this, we consider $\phi\circ{T} = \sin(\frac{\pi}{2}(1-|2u-1|))^2$

  and $S\circ\phi = 4\sin(\frac{\pi}{2}x)^{2}(1-\sin(\frac{\pi}{2}x)^2)$
\end{Example}

@@

From here we construct a multidimensional observable using the method of stacking previous observations, i.e., we create delay-coordinate map defined by
$\Phi_{k,\theta}(w) := (\theta(T^{-k}w)\ldots,\theta(T^{-1}w),\theta(w))$.  The essence of Takens theorem relates to the fact that when $k$ is sufficiently large, we can define a dynamical system on the space $\mathbb{R}^{k+1}$ whose states are $\Phi_{k,\theta}(w)$, $\Phi_{k,\theta}(Tw)$, $\Phi_{k,\theta}(T^2w)$, etc. and this dynamical system is topologically conjugate to the unknown underlying system $(W,T)$. We recall the Takens delay embedding theorem next.

@@

\begin{figure}[ht]
  \includegraphics[scale=0.25]{_takensmap.png}
  \centering
  \captionof{figure}{Schematic of Takens Embedding Theorem's usage and consequence of how iterates \ldots }
  \label{fig:takensmap}
\end{figure}
\ednote{M: Here, and throughout if you reproduce a figure, it must be stated where it was reproduced from. B: Is this satisfactory? Also, should $\tilde{F}$ be left out for now?}
\ednote{B: This is only a screenshot used as a temporary placeholder. If sufficient, I shall convert it to .eps. If not, may I perhaps have the original picture?}

@@

% \begin{figure}[ht]
%   \includegraphics[scale=0.3]{_learningfailure.png}
%   \centering
%   \caption{Illustration of a system having failed to learn the map}
%   \label{fig:supp_learning_failure}
% \end{figure}

@@

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
If $H:\overleftarrow{U}{\to}{\overleftarrow{X}_U}$ is also injective (in addition to being surjective, and hence bijective), 
it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$ and we refer to $H$ as a \emph{causal embedding} 
\ednote{M : Causal embedding a dynamical system is different from the definition of causal embedding, so please edit/delete this paragraph and the next theorem and also in the remaining part till Section 1.2}.

\begin{Theorem}
 If $g(\ldotp,x)$ is invertible and has the USP then $H$ is a causal embedding. 
\end{Theorem}
\begin{proof}
  See \cite{manjunath2021universal}.
\end{proof}

When $g$ has the USP, the diagram below illustrates the operation of the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is an observable as discussed in an above section (\ref{TakensEmbedding}).

\begin{figure}[ht]
  %\includegraphics[scale=0.3]{actionofh_H.png}
  \centering
  \label{fig:actionh_H}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.4]{_memloss_conttime.png}
  \centering
\captionof{figure}{Reproduced from \cite{manunath2021universal}. Illustration of all trajectories approaching the true solution if $g$ has the UAP}
\label{fig:memloss_conttime.png} 
\end{figure}

@@

One can therefore learn the SDD of the driven system states via $G_T$ with enough data thanks to the USP/UAP. This enables us to do at least 2 things: 
\vspace{-8mm}
\begin{itemize}[noitemsep]
\item Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined.
\item Forecast future values of $u_n$. 
\end{itemize}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.3]{_summarypictorial.png}
  \centering
  \label{fig:fig_pictorialSummary}
\end{figure}

@@

% \begin{figure}[ht]
%   \includegraphics[scale=0.3]{_gammatemp.png}
%   \centering
%   \label{fig:temp_Gamma}
% \end{figure}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.35]{_dp_setup.png}
  \centering
  \captionof{figure}{Pictorial representation of the setup of a DP. Image taken from~\cite{DPSetup}}
  \label{fig:dp_setup}
\end{figure}

>>>>

\begin{Example}\rm
  For example $\phi(x)=\sin\big(\frac{\pi}{2}x\big)^2$ is a conjugacy between two systems $Tu=1-|2u-1|$ and $Sv=4v(1-v)$  defined on $U=[0,1]$.

  Indeed, $\phi:[0,1]\to[0,1]$ is a homeomorphism and by employing simple trigonometric identities, it is easily proved that $\phi$ satisfies~\ref{eqn_conjugacy}
  \[
    \begin{aligned}[t]
      (\phi\circ{T})u 
                &=\sin^{2}\Big(\frac{\pi}{2} - \frac{\pi}{2}|2u-1|\Big) = \sin^{2}(\pi{u})=\Big(2\sin(\frac{\pi}{2})\cos(\frac{\pi}{2})\Big)^{2}=4\sin^{2}(\frac{\pi}{2}u)\Big(1-\sin^{2}\frac{\pi}{2}u\Big) \\
                                    &=({S}\circ\phi)u.
    \end{aligned}
\]
And it follows that $\phi$ is a conjugacy between the two systems.
\end{Example}

@@

From here we construct a multidimensional observable using the method of stacking previous observations, i.e., we create delay-coordinate map defined by
$\Phi_{k,\theta}(w) := (\theta(T^{-k}w)\ldots,\theta(T^{-1}w),\theta(w))$.  
The concept of an observable is understood in the sense of an observable as originally introduced by \cite{takens1981detecting, genericObservableAeyels} to refer to a probe or measurement function inserted into the system. 
The essence of Takens' theorem relates to the fact that when $k$ is sufficiently large, we can define a dynamical system on the space $\mathbb{R}^{k+1}$ whose states are $\Phi_{k,\theta}(w)$, $\Phi_{k,\theta}(Tw)$, $\Phi_{k,\theta}(T^2w)$, etc. and this dynamical system is topologically conjugate to the unknown underlying system $(W,T)$. We recall the Takens delay embedding theorem next.

@@

\begin{figure}[ht]
  \includegraphics[scale=0.25]{_takensmap.eps}
  \centering
  \captionof{figure}{Schematic of Takens Embedding Theorem's usage and consequence of how iterates \ldots }
  \label{fig:takensmap}
\end{figure}
\ednote{M: Here, and throughout if you reproduce a figure, it must be stated where it was reproduced from. B: Is this satisfactory? Also, should $\tilde{F}$ be left out for now?}
\ednote{B: This is only a screenshot used as a temporary placeholder. If sufficient, I shall convert it to .eps. If not, may I perhaps have the original picture?}

@@

% \begin{figure}[ht]
%   \includegraphics[scale=0.3]{_learningfailure.eps}
%   \centering
%   \caption{Illustration of a system having failed to learn the map}
%   \label{fig:supp_learning_failure}
% \end{figure}

@@

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
If $H:\overleftarrow{U}{\to}{\overleftarrow{X}_U}$ is also injective (in addition to being surjective, and hence bijective), 
it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$. %and we refer to $H$ as a \emph{causal embedding} 
% \ednote{M : Causal embedding a dynamical system is different from the definition of causal embedding, so please edit/delete this paragraph and the next theorem and also in the remaining part till Section 1.2}.

% \begin{Theorem}
%  If $g(\ldotp,x)$ is invertible and has the USP then $H$ is a causal embedding. 
% \end{Theorem}
% \begin{proof}
%   See \cite{manjunath2021universal}.
% \end{proof}

When $g$ has the USP, the diagram below (adopted from~\cite{Manju_Nonlinearity}) illustrates the operation of the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is also considered an observable as mentioned in the introduction of Chapter \ref{ch3}).

\begin{figure}[ht]
  \includegraphics[scale=0.3]{_actionofh_H.png}
  \centering
  \captionof{figure}{Progressive actions of $h$ and $H$ to illustrate the causal mapping. }
  \label{fig:actionh_H}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.4]{_memloss_conttime.eps}
  \centering
\captionof{figure}{Reproduced from \cite{manunath2021universal}. Illustration of all trajectories approaching the true solution if $g$ has the UAP}
\label{fig:memloss_conttime} 
\end{figure}

@@

One can therefore learn the SDD of the driven system states via $G_T$ with enough data thanks to the USP/UAP. This enables us to do at least two things: 
\vspace{-8mm}
\begin{itemize}
\item Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined.
\item Forecast future values of $u_n$. 
\end{itemize}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.3]{_summarypictorial.eps}
  \centering
  \label{fig:fig_pictorialSummary}
\end{figure}

@@

% \begin{figure}[ht]
%   \includegraphics[scale=0.3]{_gammatemp.eps}
%   \centering
%   \label{fig:temp_Gamma}
% \end{figure}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.35]{_dp_setup.eps}
  \centering
  \captionof{figure}{Pictorial representation of the setup of a DP. Image taken from~\cite{DPSetup}}
  \label{fig:dp_setup}
\end{figure}
